### 2015-01-14 fundamentals/intro.tex
cohen

An alternative to these approaches is a dynamic, agent-based simulator with an 
open platform and an ecosystem of research-driven capabilities.  
Dynamic nuclear fuel cycle analysis more realistically 
supports a range of simulation goals than static analysis 
\cite{piet_dynamic_2011}. Similarly, experience in the broader field of systems 
analysis indicates that agent-based modeling enables more flexible simulation 
control, without loss of generality \cite{macal_agent-based_2010}. Finally, openness 
allows cross-institutional collaboration, increases code robustness, and 
cultivates an ecosystem of modeling and calculation options 
\cite{softwarecarpentryresource}.  The fundamental concepts of the \Cyclus 
nuclear fuel cycle simulator capture these modern insights so that challenges 
in nuclear fuel cycle analysis can be better addressed.

@@

\Cyclus emerged from a line of tools seeking to break this practice.  
Its precursor,
\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006}, began
at \gls{LDRD} within \gls{INL} and sought 
\gls{ORION}\cite{}, and 
to provide generic regional capability.  Based on lessons learned from 
Version 1, the 
\acrshort{GENIUSv2} Version 2\cite{oliver_studying_2009,huff_geniusv2_2009} code sought to 
provide more generality and an extensible interface to facilitate 
collaboration.  The \Cyclus project then improved upon the \acrshort{GENIUSv2} 
effort by implementing increased modularity and encapsulation.  The result is  
a dynamic simulator that treats both materials and facilities discretely, with 
an architecture that permits simulations with multiple and variable levels of 
fidelity. The simulator's agent-based framework for tracking the 
transformation and trade of resources between facilities within institutions 
and regions greatly improves upon the existing fuel cycle simulators.

>>>>

An alternative to these approaches is a dynamic, agent-based simulator with an 
open platform and an ecosystem of research-driven capabilities.  
Dynamic nuclear fuel cycle analysis more realistically 
supports a range of simulation goals than static analysis 
\cite{piet_dynamic_2011}. Similarly, experience in the broader field of systems 
analysis indicates that agent-based modeling enables more flexible simulation 
control, without loss of generality \cite{macal_agent-based_2010}. Finally, openness 
allows cross-institutional collaboration, increases code robustness \cite{cohen_modern_2010}, and 
cultivates an ecosystem of modeling and calculation options.  The fundamental concepts of the \Cyclus 
nuclear fuel cycle simulator capture these modern insights so that challenges 
in nuclear fuel cycle analysis can be better addressed.

@@

\Cyclus emerged from a line of tools seeking to break this practice.  
Its precursor,
\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006}, began
as an \gls{LDRD} project within \gls{INL} and sought 
\gls{ORION}\cite{}, and 
to provide generic regional capability.  Based on lessons learned from 
Version 1, the 
\acrshort{GENIUSv2} Version 2\cite{oliver_studying_2009,huff_geniusv2_2009} code sought to 
provide more generality and an extensible interface to facilitate 
collaboration.  The \Cyclus project then improved upon the \acrshort{GENIUSv2} 
effort by implementing increased modularity and encapsulation.  The result is  
a dynamic simulator that treats both materials and facilities discretely, with 
an architecture that permits simulations with multiple and variable levels of 
fidelity. The simulator's agent-based framework for tracking the 
transformation and trade of resources between facilities within institutions 
and regions greatly improves upon the existing fuel cycle simulators.
